Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
fix abstract

Much research is currently being done to study how non-volatile and large
memory systems would change system design.  We see the need for a lightweight
tool to study such systems at scale with real workloads.  The first step
towards building such a tool is to study the scalability of existing memory
management systems.  We find that in most cases, Linux kernel memory management
scales well with large amounts of physical memory. However, workloads that
allocated many virtual memory areas can accumulate significant memory and
computational overhead due to kernel metadata.     Furthermore, in certain
situations, transparent hugepages can nullify the benefits from better TLB
reaches by inducing memory pressure earlier, even for workloads that would
otherwise not experience it.  Finally, we see that the tail
swapping latencies can account for over a majority of runtime for the
workloads we tested.

>>>>

Much research is currently being done on how non-volatile and large
memory systems would change system design.  We see the need for a lightweight
tool to study such systems at full scale with real workloads. The first step
towards building such a tool is to study the scalability of existing memory
management systems. We find that in most cases, Linux kernel memory management
scales well with large amounts of physical memory. However, workloads that
allocate many virtual memory areas can accumulate significant memory and
computational overhead due to kernel metadata. Furthermore, in some cases, 
transparent hugepages can nullify the benefits from better TLB
reach by inducing memory pressure earlier. Finally, we see that the tail
swapping latencies can account for a majority of runtime for the
workloads we tested.
